Dependent Object Types

### 2012-08-10 article.tex
subst lemma

\begin{proofsketch}
By (1) and (3), it should hold that (5) $v \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {S}$ by the subset semantics lemma.  Since (2)
holds, it should also hold that ${t} \in \rele {\min(k_1,k_2)}
{\Gamma_{12} \envplus{{x} : S}} {s_{12}} T$ by the extended
monotonicity lemma. Then, we can instantiate $x$ in the complete store
to map to what $v$ maps to. This should be fine by (5) and
monotonicity. Thus, ${t} \in \rele {\min(k_1,k_2)} {\Gamma_{12}
  \envplus{{x} : S}} {s_{12} \envplus{{x} \mapsto s_{12}(v)}}
T$. Thanks to (4), we don't actually need $x$ to be held abstract in
the environment, because it won't occur in $T$ or its expansion, so we
can use the actual type constructor of $v$, say $T_{v}$, instead of
$S$ for $x$: ${t} \in \rele {\min(k_1,k_2)} {\Gamma_{12} \envplus{{x}
    : {T_{v_2}}}} {s_{12} \envplus{{x} \mapsto s_{12}(v)}} T$. This
implies what needs to be shown.

>>>>

\begin{proofsketch}
By (1) and (3), it should hold that (5) $v \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {S}$ by the subset semantics lemma.  Since (2)
holds, it should also hold that ${t} \in \rele {\min(k_1,k_2)}
{\Gamma_{12} \envplus{{x} : S}} {s_{12}} T$ by the extended
monotonicity lemma. Then, we can instantiate $x$ in the complete store
to map to what $v$ maps to. This should be fine by (5) and
monotonicity. Thus, ${t} \in \rele {\min(k_1,k_2)} {\Gamma_{12}
  \envplus{{x} : S}} {s_{12} \envplus{{x} \mapsto s_{12}(v)}}
T$. Thanks to (4), we don't actually need $x$ to be held abstract in
the environment, because it won't occur in $T$ or its expansion, so we
can use the type of $v$ in the environment instead of
$S$ for $x$: ${t} \in \rele {\min(k_1,k_2)} {\Gamma_{12} \envplus{{x}
    : {\Gamma_{12}(v)}}} {s_{12} \envplus{{x} \mapsto s_{12}(v)}} T$. This
implies what needs to be shown.
